Code for Submission

### 2023-01-03 CodeForSubmission.Rmd
Changed pathnames in Code

```{r}
data <- read.csv("~/Desktop/MsCcHSFeedJan1MOD.csv")
scan <- read.csv("~/Desktop/MsCcHSFeedLeafScanFinal.csv", header = T)
datadead <- read.csv("~/Desktop/MsCcHSFeedJan1MOD.csv")
```

>>>>

```{r}
data <- read.csv("~/Desktop/GitHub/MsCcHSFeed/Data/MsCcHSFeedJan1MOD.csv")
scan <- read.csv("~/Desktop/GitHub/MsCcHSFeed/Data/MsCcHSFeedLeafScanFinal.csv", header = T)
datadead <- read.csv("~/Desktop/GitHub/MsCcHSFeed/Data/MsCcHSFeedJan1MOD.csv")
```
